Nonlinear Dendritic Coincidence Detection for Supervised Learning

### 2021-05-09 notes/draft_article.tex
.

\usepackage[numbers]{natbib}
\bibliographystyle{nourlplainnat.bst}

@@

		It should be noted, though, that to a certain extent, the objective function is not
		scale-invariant in the sense that the prior distributions of both proximal 
		and distal inputs need a certain mean and variance to cover a region of input
		state for which the described effects can take place. This, however, is 
		guaranteed by the homeostatic processes acting simultaneously on the gains
		and biases.

@@

		The idea of target-backpropagation in multi-layered networks
		has already been proposed in different variants
		\cite{Bengio2014,Lee2015,Guerguiev2017}. Yet, all of these approaches
		assume a learning rule being dependent on an explicit error term 
		between top-down and bottom up signals guiding plasticity in some form
		or another. In this work, we considered an alternative approach, that is,
		the correlation between proximal and distal input as a maximization
		objective.

@@

>>>>

\usepackage[numbers]{natbib}
\bibliographystyle{nourlplainnat.bst}
%\bibliographystyle{abbrvnat}

@@

		It should be noted, though, that to a certain extent, the objective function is not
		scale-invariant (as would be e.g.\ if the squared error was used) in the sense 
		that the prior distributions of both proximal 
		and distal inputs need a certain mean and variance to cover a region of input
		states for which the described effects can take place. As a counterexample,
		one could imagine that the input samples only covered a flat of $\mathcal{L}_p$, as
		for example in Fig.~\ref{fig:obj_func} on the left, leading to a zero average gradient. 
		This is prevented, however, by the homeostatic processes acting simultaneously on the gains
		and biases.

@@

@@

		The idea of target-backpropagation in multi-layered networks
		has already been proposed in different variants
		\cite{Bengio2014,Lee2015,Guerguiev2017}. Yet, all of these approaches
		assume a learning rule being dependent on an explicit error term 
		between top-down and bottom up signals guiding plasticity in some form
		or another. In this work, we considered an alternative approach, that is,
		the correlation between proximal and distal input as a maximization
		objective, in combination with homeostatic adaptation rules that regulate
		proximal and distal inputs into a desired ``working regime'', 
		see Sect.~\ref{sect:Obj_Func}. 
		Since $I_p$ is a linear projection of the 
		proximal input space, maximizing the correlation between
		$I_p$ and $I_d$ can be regarded as a form of canonical correlation
		analysis (CCA) \cite{Haerdle2007}. The idea of investigating CCA as a
		possible mode of synaptic learning has previously been investigated by
		\citet{Haga2018}. Interestingly, according to the authors, a 
		BCM-learning term in the plasticity dynamics accounts for principal component
		analysis in the input space, while CCA requires an additional multiplicative
		term between local basal and apical activity. In contrast, our results
		indicate that such a multiplicative term is not required to drive basal
		synaptic plasticity towards a maximal alignment between basal and apical
		input, even in the presence of distracting principal components.

		As we did not include higher-dimensional distal input patterns, it
		remains an open question how target signals would be formed in
		multi-layered network structures. However, as previous works have
		indicated, random top-down weights can be sufficient for
		successful credit assignment and learning \cite{Lillicrap2016,Guerguiev2017}.
		Therefore, our results could potentially also be transferred to deeper
		network structures, where plasticity is guided by local errors between
		top-down and bottom-up signals.
